Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated

### 2017-02-23 ms_pre_post.Rmd
A bit more detail to the sampling

Each male's value with respect to each focal female is then divided by the sum of all $Q^{m}_{ij}$ values across all males with respect to that female, thereby assigning each male a relative perceived quality $q^{m}_{ij}$, which is constrained to values between zero and one. The value of $q^{m}_{ij}$ then defines the probability that a focal female mates with the male. Mating is realised by placing each $q^{m}_{ij}$ value into a vector whose elements sum to unity. A new vector of identical size is then created where each element equals the summation of all previous elements in the original vector of $q^{m}_{ij}$ values. Because each element in the vector corresponds to a unique male, a random uniform number between zero and one can identify a female's realised mate. This realisation is enacted by identifying the element in the vector that is closest to, but not less than, the random uniform number. Mating is therefore stochastic, and females do not always mate with the male of the highest $q^{m}_{ij}$. For polyandrous females that choose multiple mates (i.e., $N_{mates}>1$), mates are chosen iteratively such that $Q^{m}_{ij}$ and $q^{m}_{ij}$ are re-calculated for each additional mate choice, and with $Q^{m}_{ij}$ and therefore $q^{m}_{ij}$ values of already chosen males set to zero to ensure mate sampling without replacement. In the unlikely event that a female's $N_{males}$ exceeds the total number of available males, then she simply mates with all males.

>>>>

Each male's value with respect to each focal female is then divided by the sum of all $Q^{m}_{ij}$ values across all males with respect to that female, thereby assigning each male a relative perceived quality $q^{m}_{ij}$, which is constrained to values between zero and one. The value of $q^{m}_{ij}$ then defines the probability that a focal female mates with the male. Mating is realised by placing each $q^{m}_{ij}$ value into a vector whose elements sum to unity. A new vector of identical size is then created where each element equals the summation of all earlier position elements in the original vector of $q^{m}_{ij}$ values (such that the first element is zero and last is a number $\leq 1$). Because each element in the vector corresponds to a unique male, a random uniform number between zero and one can identify a female's realised mate. This realisation is enacted by identifying the element in the vector that is closest to, but not less than, the random uniform number. Mating is therefore stochastic, and females do not always mate with the male of the highest $q^{m}_{ij}$. For polyandrous females that choose multiple mates (i.e., $N_{mates}>1$), mates are chosen iteratively such that $Q^{m}_{ij}$ and $q^{m}_{ij}$ are re-calculated for each additional mate choice, and with $Q^{m}_{ij}$ and therefore $q^{m}_{ij}$ values of already chosen males set to zero to ensure mate sampling without replacement. In the unlikely event that a female's $N_{males}$ exceeds the total number of available males, then she simply mates with all males.
